### 2023-03-07 main.tex
reaction
fixedReaction
after fix

thus (\ref{bulkDuality}) is proved.\\

@@

\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle

@@

\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle

@@

\subsection{Bethe equations}
Describe eigenvalues of $T_0(x)$ following.
\cite{belliard2}
\section{Conclusion}

>>>>

thus (\ref{bulkDuality}) is proved. \\

@@

\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle

@@

\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle

@@

{\color{blue}This second property can be proved by using a lower weight representation }
% \end{itemize}
We prove the ansatz:
	T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
	\\&+
	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0} 
	\\&+\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}+1}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\\&+\ldots +
	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}+1}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
we replace $k_{i}\to k_{i}+1$ $\forall i\in\{2,\ldots,N\}$ in the proper summation. Then,
	T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
	\\&+
	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\\&+\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2}-1,\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\\&+\ldots
	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}-1}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\\&+
	\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{3}^{k_{3}}\Delta_{N}^{k_{N}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{m_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\\&+\ldots +
	\Delta_{N}^{m_{N}+1}\sum_{k_{2}=0}^{m_{3}}\ldots\sum_{k_{N-1}=0}^{m_{N-1}}\Delta_{3}^{k_{2}}\Delta_{N-1}^{k_{N-1}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
We use prperties \eqref{SecondProperty} and \eqref{FirstProperty}:
		T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
	\\&+
	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\\&+\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\\&+\ldots +
	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=
		\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
	\\&+
	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle

For $i\neq 1$ we have
\begin{equation}
\begin{split}
 \sum_{i,j=2}^N [E_{ij}E_{ji},E_{k1}]&=\sum_{i,j=2}^N E_{ij} [E_{ji},E_{k1}]+\sum_{i,j=2}^N  [E_{ij},E_{k1}]E_{ji}=\sum_{j=2}^N( E_{kj} E_{j1}+ E_{j1} E_{kj})
\\&=\sum_{j=2}^N( 2E_{kj} E_{j1}+ [E_{j1}, E_{kj}])=2\sum_{j=2}^N E_{kj} E_{j1}-(N-1)E_{k1}
 \end{split}
\end{equation}

\subsection{Bethe ansatz solution}
Describe eigenvalues of $T_0$ following 
\cite{Belliard2} 
\section{Conclusion}
